---
title: "R_exam_2021"
author: "Prati"
date: "07 10 2021"
output: html_document
---
setwd("C:/Users/pba081/OneDrive - University of Bergen/PhD_88/Courses/R_Autumn21")
####Installing tidyverse and here
```{r}
install.packages("tidyverse")
library(tidyverse)
```
```{r}
install.packages("here")
library(here)
```
####reading my working data
```{r}
myData <- read.delim("exam_data.txt")
```
####exploring data
```{r}
head(myData)
```

```{r}
tail(myData, 20)
```
###summary
```{r}
summary(myData)
```
####separate first column
```{r}
myData %>%
  separate(col = subject, into = c("id", "name"), sep = "-")
```
### view data
```{r}
view(myData)
```

### installing additional packages
```{r}
install.packages(c("finalfit","skimr","naniar"))
```
###
```{r}
finalfit::ff_glimpse(myData)
```
###exploring duplicate column

```{r}
skimr::skim(myData)
```

```{r}
summary(myData)
```
###some columns are duplicate
```{r}
myData %>% 
  select(test_id, X1_test_id)
```

###removing duplicate columns
```{r}
myData %>% 
  select(-X1_test_id)
```
```{r}
view(myData)
```

```{r}
myData %>% 
  mutate(age_female = if_else(age_female > 1, "0", "1"))
```

```{r}
view(myData)
```

```{r}
myData <-
  myData %>% 
  mutate(ID = 1:n())
```

```{r}
myData
```
```{r}
glimpse(myData)
```


```{r}
myData %>% 
  count(result)
```

```{r}
myData %>% 
  count(demo_group)
```


####missing values in the dataset
```{r}
naniar::gg_miss_var(myData)
```
###yes there are missung values for subject, age and gender, payor_group and patient_class.

```{r}
myData %>% 
  count(drive_thru_ind)
```
##Answer No. 4
```{r}
myData %>% 
  filter(drive_thru_ind == "1") %>%
  count(result)
```
####No there are no more negative tests in the drive-through.

###short note on RMD:RMD is a R markdown file which is used to better create complete reports. It uses text, code and output side by side. RMD files are easily reproducible.

